Case study validations of automatic bullet matching

### 2018-11-04 index.Rmd
Some explanation of features. Need better CCF stuff...

## Explain RF score, CC and CMS

>>>>

## Statistics for Matching Aligned Signatures

\svp{Firearms examiners often use consecutive matching striae (CMS) to describe the strength of a match. CMS as used by examiners counts only peaks as striae, as it is difficult to assess vallleys and peaks separately when using a comparison scope.  If there are at least 6 consecutive matching striae, the bullets are considered to be a good match \citep{biasotti_firearms_1997,nichols_scientific_2006}, according to criteria used by FTEs. There are some differences between CMS as defined by FTEs and the method used in \citet{asos} includes both peaks and valleys, as it is easier to assess the features separately using cross-sections. XXX Should we go into this, or just leave it as is?
}

\svp{Cross-correlation between two signatures $S_1(x)$ and $S_2(x)$, $$CC(S_1, S_2, z) = \lim_{L\rightarrow\infty}\left(\frac{1}{L} \int_{-L/2}^{L/2} S_1(x)S_2(x + z) dx \right)/[R_1R_2]$$ where $z$ is the shift difference between the two sequences and $R_1$ and $R_2$ are the root mean square roughness for the two signature \citep{vorburgerApplicationsCrosscorrelationFunctions2011}. We maximize $CC$ over values of $z$ to determine the best alignment; this maximal value is used to assess the match strength between the two sequences. XXX algorithm for calculating with missing values?}

\svp{XXX No idea what to say about the RF other than what's above?}
